A comparison of classification algorithms applied to the Adult Database

### 2009-12-08 report/final.tex
CN2 paper.
some rework

@@

>>>>

After the data as been pre-processed,
we will build the classifier using the train data set.
Once the classifier is trained, it will be used to classify both the train and test data.

Various performance metrics for both classification results will be registered:
error rate, mean absolute error, kappa statistic, etc.

@@

\bibitem{cn2}
Peter Clark and Tim Niblett. The CN2 induction algorithm. 1988.
